Posterior summarisation in Bayesian phylogenetics using Tracer 1.7

### 2017-12-15 manuscript/tracer17.tex
comment-out large box-and-wisker plot

\begin{figure}[ht]
\subfigure[TangHuLu chart]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/rabv-integerjointmarginal.pdf}}
\subfigure[Marginal density]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/rabv-integermarginaldensity.pdf}} \\
\subfigure[Scatter plot]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/rabv-correlation.pdf}}
\subfigure[Correlation plot]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/rabv-joint-real.pdf}} \\
\subfigure[Box-and-whisker plot]{\includegraphics[width = .465\textwidth, height = 3cm]{./figures/rabv-catreal.pdf}}
\caption{Joint marginal and marginal density plots of: (a) two integer variables through a TangHuLu chart; (b) frequency plots the marginal density of multiple integer or categorical variables; (c) classic scatter or correlation plot for two continuous variables; (d) large correlation matrices for multiple ($> 2$) continuous variables; (e) box-and-whisker plots for the joint marginal distribution of a continuous and an integer or categorical variable.}
\label{fig:4tabs}
\end{figure}

Performing BSSVS in a discrete phylogeographic approach provides us with parameters of the integer and categorical trace type.
While a single parameter of such types can easily be visualised using a frequency plot, we have developed a TangHuLu chart to visualise the joint probability between two integer or categorical traces using coloured bubbles (see Figure \ref{fig:4tabs}:a).
The size of circle drawn is proportional to the joint probability, %the blue coloured circle is in the credible set of given a probability threshold default to 0.95, the red is in the set not in the credible set.
with the tile background being coloured if there is in fact a circle, to enhance visibility.
%The coloured background can also help to show the area of the credible set and non-credible set.
Multiple integer parameters can also be visualised using marginal density plots (see Figure \ref{fig:4tabs}:b), with a different colour scale being assigned to each parameter.
Both figures show a clear overlap in the number of non-zero transition rates in the discrete trait models for host and location, as identified using a BSSVS procedure.
The visualisation options for integer or categorical parameters are complemented with popular plots for continuous variables, such as a scatter or correlation plot (see Figure \ref{fig:4tabs}:c) for two continuous variables, which indicates a strong positive correlation between the clock rates of both discrete trait models.
We also provide an extension of such a scatter plot for multiple (i.e. more than two) continuous variables (see Figure \ref{fig:4tabs}:d; \citet{Murdoch}), which makes use of coloured ellipses to indicate the strength of correlation between each pair of continuous variables.
Colour gradients indicate the strength and direction of the correlation, with a colour gradient from white to dark blue indicating increasingly strong correlation and a colour gradient from white to dark red indicating increasingly strong anti-correlation.
Additionally, the strength of correlation is reflected in the shape of the ellipse drawn, with no correlation being drawn as a circle and perfect (anti-)correlation being drawn as a line.
Finally, in order to display the joint marginal distribution between a continuous variable and an integer or categorical variable, we make use of box-and-whisker plots.
Using such a plot (Figure \ref{fig:4tabs}:e), we can infer that the range of the non-zero transition rates can depend on the ancestral location state inferred at the root of the underlying phylogeny.

>>>>

\begin{figure}[ht]
\subfigure[TangHuLu chart]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/rabv-integerjointmarginal.pdf}}
\subfigure[Marginal density]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/rabv-integermarginaldensity.pdf}} \\
\subfigure[Scatter plot]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/rabv-correlation.pdf}}
\subfigure[Correlation plot]{\includegraphics[width = .23\textwidth, height = 3cm]{./figures/rabv-joint-real.pdf}} \\
%\subfigure[Box-and-whisker plot]{\includegraphics[width = .465\textwidth, height = 3cm]{./figures/rabv-catreal.pdf}}
\caption{Joint marginal and marginal density plots of: (a) two integer variables through a TangHuLu chart; (b) frequency plots the marginal density of multiple integer or categorical variables; (c) classic scatter or correlation plot for two continuous variables; (d) large correlation matrices for multiple ($> 2$) continuous variables.
%; (e) box-and-whisker plots for the joint marginal distribution of a continuous and an integer or categorical variable.
}
\label{fig:4tabs}
\end{figure}

Performing BSSVS in a discrete phylogeographic approach provides us with parameters of the integer and categorical trace type.
While a single parameter of such types can easily be visualised using a frequency plot, we have developed a TangHuLu chart to visualise the joint probability between two integer or categorical traces using coloured bubbles (see Figure \ref{fig:4tabs}:a).
The size of circle drawn is proportional to the joint probability, %the blue coloured circle is in the credible set of given a probability threshold default to 0.95, the red is in the set not in the credible set.
with the tile background being coloured if there is in fact a circle, to enhance visibility.
%The coloured background can also help to show the area of the credible set and non-credible set.
Multiple integer parameters can also be visualised using marginal density plots (see Figure \ref{fig:4tabs}:b), with a different colour scale being assigned to each parameter.
Both figures show a clear overlap in the number of non-zero transition rates in the discrete trait models for host and location, as identified using a BSSVS procedure.
The visualisation options for integer or categorical parameters are complemented with popular plots for continuous variables, such as a scatter or correlation plot (see Figure \ref{fig:4tabs}:c) for two continuous variables, which indicates a strong positive correlation between the clock rates of both discrete trait models.
We also provide an extension of such a scatter plot for multiple (i.e. more than two) continuous variables (see Figure \ref{fig:4tabs}:d; \citet{Murdoch}), which makes use of coloured ellipses to indicate the strength of correlation between each pair of continuous variables.
Colour gradients indicate the strength and direction of the correlation, with a colour gradient from white to dark blue indicating increasingly strong correlation and a colour gradient from white to dark red indicating increasingly strong anti-correlation.
Additionally, the strength of correlation is reflected in the shape of the ellipse drawn, with no correlation being drawn as a circle and perfect (anti-)correlation being drawn as a line.
%Finally, in order to display the joint marginal distribution between a continuous variable and an integer or categorical variable, we make use of box-and-whisker plots.
%Using such a plot (Figure \ref{fig:4tabs}:e), we can infer that the range of the non-zero transition rates can depend on the ancestral location state inferred at the root of the underlying phylogeny.
